Dominance Regions for Rank Two Cluster Algebras

### 2022-05-11 dominance_regions.tex
Minor section 7 edits

  In this section we compare our main result with the construction of \cite{RSW19} in the case $b=c=2$.
  To match conventions, in this section, we work over an algebraically closed field $\kk$ of characteristic 0.
  Because the exchange matrix is full rank there is no loss of generality in continuing to work in the coefficient-free case.
  We will identify the family of bases from Theorem \ref{th:dominance} with the continuous family of bases of $\cA(2,2)$ constructed in \cite{RSW19} from generalized minors which we recast here with the current notation.

  \begin{theorem}[{\cite[Theorem 4.6]{RSW19}}]
    Choose a point $\bfa\in(\kk^\times)^n$ for each $n\geq1$.
    Then the elements 
    \[
      x_{(n,-n)}^{\bfa}:= x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} \sum\limits_{r=0}^\ell {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
    \]
    with
    \[
      S_{\bfa,r}=\sum\limits_{\substack{I,J\subseteq[1,n]\\|I|=r=|J|\\ I\cap J=\varnothing}}\frac{\prod_{i\in I} a_i}{\prod_{j\in J} a_j}
    \]
    together with all cluster monomials form a linear basis of $\cA(2,2)$.
  \end{theorem}

@@

	\begin{theorem}
    \[
      x_{(n,-n)}^{\bfa}
      =
      \sum_{r=0}^{\lfloor \frac{n}{2} \rfloor}
      S_{\bfa,r}
      x_{(n-2r,-n+2r)}^{ge}
    \]
  \end{theorem}
  \begin{proof}
    \begin{align*}
      x_{(n,-n)}^{\bfa}
      & =
      x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} \sum\limits_{r=0}^\ell {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
    \end{align*}
    From the second binomial coefficient we deduce that $n-2r$ is positive so the second sum runs up to $\lfloor \frac{n}{2} \rfloor$.
    \begin{align*}
      x_{(n,-n)}^{\bfa}
      & =
      x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} \sum\limits_{r=0}^{\lfloor \frac{n}{2} \rfloor} {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
      \\
      & =
      \sum\limits_{r=0}^{\lfloor \frac{n}{2} \rfloor} S_{\bfa,r}\, x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} {\ell-r\choose k} {n-2r\choose \ell-r}  x_0^{2(\ell-k)} x_1^{2(n-\ell)}
      \\
      & =
      \sum\limits_{r=0}^{\lfloor \frac{n}{2} \rfloor} S_{\bfa,r}\, x_0^{-n+2r} x_1^{-n+2r} \sum_{0 \leq k \leq \ell \leq n} {\ell-r\choose k} {n-2r\choose \ell-r}  x_0^{2(\ell-k-r)} x_1^{2(n-\ell-r)}
  \end{align*}
  \end{proof}

>>>>

  In this section we compare our main result with the construction of \cite{RSW19} in the case $b=c=2$.
  To match conventions, in this section, we work over an algebraically closed field $\kk$ of characteristic 0.
  Because the exchange matrix is full rank there is no loss of generality in continuing to work in the coefficient-free case.
  We will identify the family of bases in Theorem \ref{th:dominance} with the continuous family of bases of $\cA(2,2)$ constructed in \cite{RSW19} from generalized minors, which we recast here with the current notation.

  \begin{theorem}[{\cite[Theorem 4.6]{RSW19}}]
    Choose a point $\bfa\in(\kk^\times)^n$ for each $n\geq1$.
    Then, together with all cluster monomials, the elements 
    \[
      x_{(n,-n)}^{\bfa}:= x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} \sum\limits_{r=0}^\ell {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
    \]
    with
    \[
      S_{\bfa,r}=\sum\limits_{\substack{I,J\subseteq[1,n]\\|I|=r=|J|\\ I\cap J=\varnothing}}\frac{\prod_{i\in I} a_i}{\prod_{j\in J} a_j}
    \]
    form a linear basis of $\cA(2,2)$.
  \end{theorem}

@@

	\begin{theorem}
    \[
      x_{(n,-n)}^{\bfa}
      =
      \sum_{r=0}^{\lfloor n/2 \rfloor}
      S_{\bfa,r}
      x_{(n-2r,-n+2r)}^{ge}
    \]
  \end{theorem}
  \begin{proof}
    \begin{align*}
      x_{(n,-n)}^{\bfa}
      & =
      x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} \sum\limits_{r=0}^\ell {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
    \end{align*}
    From the second binomial coefficient we deduce that $n-2r$ is positive so the second sum runs up to $\lfloor n/2 \rfloor$.
    \begin{align*}
      x_{(n,-n)}^{\bfa}
      & =
      x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} \sum\limits_{r=0}^{\lfloor n/2 \rfloor} {\ell-r\choose k} {n-2r\choose \ell-r} S_{\bfa,r}  \, x_0^{2(\ell-k)} x_1^{2(n-\ell)}
      \\
      & =
      \sum\limits_{r=0}^{\lfloor n/2 \rfloor} S_{\bfa,r}\, x_0^{-n} x_1^{-n} \sum_{0 \leq k \leq \ell \leq n} {\ell-r\choose k} {n-2r\choose \ell-r}  x_0^{2(\ell-k)} x_1^{2(n-\ell)}
      \\
      & =
      \sum\limits_{r=0}^{\lfloor n/2 \rfloor} S_{\bfa,r}\, x_0^{-n+2r} x_1^{-n+2r} \sum_{0 \leq k \leq \ell \leq n} {\ell-r\choose k} {n-2r\choose \ell-r}  x_0^{2(\ell-k-r)} x_1^{2(n-\ell-r)}
  \end{align*}
  \end{proof}
